Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-28 paper/ms.tex
Update fig and caption

\begin{deluxetable*}{ccccccc}
\tablehead{\colhead{name} & \colhead{initial position} & \colhead{initial
velocity} & \colhead{$J_r$} &
\colhead{$L_z$} & \colhead{$J_z$} & \colhead{$z_{\text{max}}$}\\ \colhead{ } &
\colhead{$\mathrm{kpc}$} & \colhead{$\mathrm{km}/\mathrm{s}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{pc}$}}
\startdata 
thin & $(8, 0, 0)$ & $(0, -190, 10)$ & 40.3 & -1520 & 0.69 & 122 \\
thick & $(8, 0, 0)$ & $(0, -190, 30)$ & 32.5 & -1520 & 23.0 & 425 \\ 
halo & $(8, 0, 0)$ & $(0, -190, 50)$ & 32.8 & -1520 & 529.1 & 854
\enddata
\label{tab:orbits}
\end{deluxetable*}

@@

\begin{figure*}
\plotone{fig/schmactions_one_orbit.pdf}
\caption{The artificial phase-dependence in the observed actions induced by an
error in the Galactocentric coordinate system. We consider here an orbit with
initial position $(8,0,0)\,\kpc$ and initial velocity $(0,-190,30)\,\kms$.
This corresponds to an orbit with actions $(J_r, L_z, J_z) = (37.9, -1520,
7.0)\,\actunit$ and $z_{\text{max}}=425\,\pc$. We integrate the orbit
according to the procedure laid out in Section~\ref{ssec:action_comp}. Then,
we subtract $100\,\pc$ from the $z$ value of each position in the orbit,
corresponding to an erroneous observer assuming a midplane that is off by
$100\,\pc$. We then allow our (immortal) observer to observe the orbit over
$1\,\Gyr$ and perform the same orbit integration procedure at each timestep,
and report the values of the actions. The computation of $L_z$ is pristine to
errors in $z$, with only numerical artifacts remaining. Only small errors are
induced in $J_r$, with the middle $90\%$ of values over the $\Gyr$ being
$\sim6\%$ of the true $J_r$. As expected, large errors are induced in $J_z$,
with the middle $90\%$ of values being $\sim85\%$ of the true $J_z$.}
\label{fig:one_orbit_wrong_ref}
\end{figure*}

>>>>

\begin{deluxetable*}{ccccccc}
\tablecaption{Description and names of the three orbits considered in this work.}
\tablehead{\colhead{name} & \colhead{initial position} & \colhead{initial
velocity} & \colhead{$J_r$} &
\colhead{$L_z$} & \colhead{$J_z$} & \colhead{$z_{\text{max}}$}\\ \colhead{ } &
\colhead{$\mathrm{kpc}$} & \colhead{$\mathrm{km}/\mathrm{s}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{pc}$}}
\startdata 
thin & $(8, 0, 0)$ & $(0, -190, 10)$ & 40.3 & -1520 & 0.69 & 122 \\
thick & $(8, 0, 0)$ & $(0, -190, 30)$ & 32.5 & -1520 & 23.0 & 425 \\ 
halo & $(8, 0, 0)$ & $(0, -190, 50)$ & 32.8 & -1520 & 529.1 & 854
\enddata
\label{tab:orbits}
\end{deluxetable*}

@@

\begin{figure*}
\plotone{fig/schmactions_one_orbit.pdf}
\caption{The artificial phase-dependence in the observed actions induced by an
error in the Galactocentric coordinate system. We consider here the thick disk
orbit, which has actions of $(J_r, L_z, J_z) = (37.9, -1520, 7.0)\,\actunit$
and $z_{\text{max}}=425\,\pc$ (see Table~\ref{tab:orbits}). We integrate the
orbit according to the procedure laid out in Section~\ref{ssec:action_comp}.
Then, we subtract $100\,\pc$ from the $z$ value ({\em upper panels}) or the
$x$ value ({\em lower panels}) of each position in the orbit, corresponding to
an erroneous observer assuming a midplane ({\em upper}) or solar radius ({\em
lower}) that is off by $100\,\pc$. We then allow our (immortal) observer to
observe the orbit over $1\,\Gyr$ and perform the same orbit integration
procedure at each timestep, and report the values of the actions. The
computation of $L_z$ is pristine to errors in $z$, with only numerical
artifacts remaining. Only small errors are induced in $J_r$, with the middle
$90\%$ of values over the $\Gyr$ being $\sim6\%$ of the true $J_r$. As
expected, large errors are induced in $J_z$, with the middle $90\%$ of values
being $\sim85\%$ of the true $J_z$.}
\label{fig:one_orbit_wrong_ref}
\end{figure*}
